`flippant` --- An `R` package for the automated analysis of dithionite scramblase

### 2016-07-16 inst/manuscript/manuscript.rmd
R-enable explicitly loading flippant to achieve formated code-chunk presentation;

```{r setting_up_r, echo = FALSE, message = FALSE}
library(magrittr, quietly = TRUE)
flippant_dependencies <- packageDescription("flippant",fields=c("Depends","Imports")) %>%
  unlist(use.names = FALSE) %>%
  stringi::stri_split(regex = ",", omit_empty = TRUE) %>%
  unlist(use.names = FALSE) %>%
  stringi::stri_replace_all(replacement = "", regex = "\\s*\\(.*\\)\\s*", omit_empty = TRUE) %>%
  stringi::stri_replace_all(replacement = "", regex = "\\s*", omit_empty = TRUE) %>%
  tail(n=length(.) - 1) %>%
  sort() %>%
  ( function(x){
    paste0(
      c(
        "`",
        paste0(head(x, n = length(x) - 1), collapse = "`, `"),
        "` and `",
        tail(x, n = 1),
        "`"),
      collapse = "")} )

>>>>

```{r setting_up_r, echo = FALSE, message = FALSE}
library(flippant, quietly = TRUE)
library(magrittr, quietly = TRUE)
flippant_dependencies <- packageDescription("flippant",fields=c("Depends","Imports")) %>%
  unlist(use.names = FALSE) %>%
  stringi::stri_split(regex = ",", omit_empty = TRUE) %>%
  unlist(use.names = FALSE) %>%
  stringi::stri_replace_all(replacement = "", regex = "\\s*\\(.*\\)\\s*", omit_empty = TRUE) %>%
  stringi::stri_replace_all(replacement = "", regex = "\\s*", omit_empty = TRUE) %>%
  tail(n=length(.) - 1) %>%
  sort() %>%
  ( function(x){
    paste0(
      c(
        "`",
        paste0(head(x, n = length(x) - 1), collapse = "`, `"),
        "` and `",
        tail(x, n = 1),
        "`"),
      collapse = "")} )
